Word learning at the semantics pragmatics interface

### 2020-03-10 paper/supplementary_material.Rmd
move supplement forward

@@

First empirical studies. Then the general modelling framework and the pragmatic model in detail. Then we turn to results. First prediction (i.e. which model makes the best predictions about combination based on only the experiments for the individual inferences) then explanation, that is, if we use all the data that we have, how can we best explain what is happening. Here we fit the models to the combination data. We consider two hypothesis. First our pragmatic model in which the Me inference is conditional on the prior, second a mixture model in which the two inferences are computed separately and mixed by a certain ratio. We also explore a developmental mixture model in which we allow the mixture component to change with age.

@@

The first experiment tested the so called mutual exclusivity inference in children between 2 and 5 years of age. The general phenomena is that when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g. @markman1988children]. A range of explanations have been put forward for the cogntive basis of this inference [see @lewis2020-me for a discussion]. Here, we treat the mutual exclusivity inference as pragmatic [e.g. @clark1987principle]. The inference process is specified in the model below.

The first goal of this experiment was to quantify developmental change in the age range tested. The second goal of Experiment 1 was to test the role of semantic knowledge [cf. @lewis2020-me]. The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object. That is, when the familiar object is an object for which chldren are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object. To test this, we systematically varied the familair object that was presented with the novel object.

@@

We tested a total number of `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls). Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1). All children were recruited from the floor of a Children’s museum in San José, California, USA. This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status. Parents consented to their children’s participation and provided demographic information. All experiments were approved by the Stanford Institutional Review Board (protocolno. 19960)

@@

The experiment was presented as an interactive pricture book on a tablet computer [@frank2016using]. Figure \@ref(fig:fig1)A shows the general setup. Children saw an animal between two tables. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests. Each experiment started with two training trials in which the speaker requested a known object (car and ball).

In Experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for te purpose of the study). The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?". Children responded by touching one of the objects. The location of the novel object (left or right table) and the animal character were counterbalanced. Each child received 12 trials, one with each familiar object. The novel object also chnaged from trial to trial. We coded as correct choice if children chose the novel object as the referent of the novel word.

@@

Each child completed 12 trials, each with a different familiar and a different novel object. Familiar objects were selected to vary along the dimension of how likely children were to know the word for each object. This including objects that most 2-year-olds could name (e.g. a duck) as well as objects that only very few 5-year-olds could name (e.g. a pawn). The selection was based on age of acquition ratings from Kuperman and colleagues [-@kuperman2012age]. While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned. Figure \@ref(fig:fig2)A shows the objects used in the experiment. We induced this variation to estimate the role of semantic knowledge in a mutual excusivity inference.

@@

prior_me <- c(prior(normal(0, 10), class = Intercept),
           prior(normal(0, 10), class = b),
           prior(cauchy(0, 1), class = sd))

bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
                    data = me_data, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          prior = prior,
          cores = 4,
          chains = 4,
          iter = 5000)%>%
  saveRDS(.,"../saves/bm_me.rds")

@@

As a second step, we investiagted how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a] with default priors. The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`\footnote{We did not pre-register agent as a random effect, but decided to included it to be consistent with Experiment 2 and 3.}. That is, we modeled an overall slope for age (continous, anchored at the minimum) and the object specific developmental trajcetories as deviations from the overall intercept and slope (random effects). The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and shows that there was substantial variation between them. Figure \@ref(fig:fig2)C shows the correaltion between rated age of acquisition and object specific model intercept. The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the mutual exclusivity inference depended on age as well as the familiar object.

@@

Here we tested children's sensitivity to common ground that is build up over the course of a conversation. In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two]. The main goal of the experiment was to measure how children's sensitivity to common grouns changes with age.

@@

The general setup was the same as in Experiment 1. The speaker was positioned between the tables. There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second novel object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B). The positioning of the novel object in the beginning of the experiment as well as the location the speaker turned to first was counterbalanced. Children received five trials, each with a different pair of novel objects. We coded as correct choice if chidlren chose the object that was new to the speaker as the referent of the novel word.

@@

```{r}
# bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = prior_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_cg.rds")

@@

To directly investiagte whether children's response changed with age, we modeled the trial by trial data using a Bayesian GLMM (formula: `correct ~ age + (1 | id) + (age | speaker)`, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)). The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_cg%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_cg%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_cg%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`, see Figure \@ref(fig:fig3)). Older children were more likely to chose the object that was new to the speaker as the referent of the novel word, suggesting that the sensitivity to common ground in this context increases with age.

## Experiment 3: Combination

Experiment 3 combined the procedures from Experiment 1 and 2. As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but alo the role that each object (novel and familiar) had played in the preceeding interaction. Combining the two procedures created two conditions: In the *congruent* condition, the novel object was also the object that was new to the speaker. In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent. In the *incongurent condition*, the familiar object was new to the speaker. Int his case, the two inferences pointed to different objects. The main focus of the overall study was to model how children integrate and balance these different inforamtion sources. We investigate this question in depth in the [modelling](#model) section below. Here, we limit the discussion to whether children differentiated between the two conditions.

@@

@@

@@

prior_comb <- c(prior(normal(0, 5), class = Intercept),
           prior(normal(0, 5), class = b),
           prior(cauchy(0, 1), class = sd))

bm_comb <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | item)+ (age * alignment | agent),
                    data = comb_data, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          prior = prior_comb,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  saveRDS(.,"../saves/bm_comb.rds")

@@

plot_comb <- ggplot(plot_comb_map, aes(x=age,y = y, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(data = comb_data%>%left_join(aoa_ratings)%>%ungroup()%>%mutate(item = fct_reorder(factor(item), mean_aoa)), aes(x = age_num, y= correct, col = item), width = .00, height = .04, alpha = .2)+
  geom_line(size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~condition)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

@@

@@

Comparison to chance not meaningful

@@

## loci of development

Semantic Knowledge, Speaker Optimality, Prior sensitivity. Each correspond to an age sensitive parameter in our model. That is they change as a function of age. We assume that the integration process remains constant over time.

@@

@@

@@

Estimate parameters based on me data and prior data. The models considered belwo make differential use of theses parameters. Basically, one full model and the rest are lesion model

### Pragmatic model

@@

semantic knowledge is only a function of age and not specific to the item. Roughyl corresponds to. If children are vaguely familiar with an object, the make the ME inference regardless of the individual object

@@

range of log like accross chains and then model comparison

@@

### Pragmatic model

>>>>

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

@@

First empirical studies. Then the general modelling framework and the pragmatic model in detail. Then we turn to results. First prediction (i.e. which model makes the best predictions about integration based on only the experiments for the individual inferences) then explanation, that is, if we use all the data that we have, how can we best explain what is happening. Here we fit the models to the integration data. We consider two hypothesis. First our pragmatic model in which the Me inference is conditional on the prior, second a mixture model in which the two inferences are computed separately and mixed by a certain ratio. We also explore a developmental mixture model in which we allow the mixture component to change with age.

@@

The first experiment tested the so called mutual exclusivity inference in children between 2 and 5 years of age. The general phenomena is that when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g. @markman1988children]. A range of explanations have been put forward for the cognitive basis of this inference [see @lewis2020-me for a discussion]. Here, we treat the mutual exclusivity inference as pragmatic [e.g. @clark1987principle]. The inference process is specified in the model below.

The first goal of this experiment was to quantify developmental change in the age range tested. The second goal of Experiment 1 was to test the role of semantic knowledge [cf. @lewis2020-me]. The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object. That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object. To test this, we systematically varied the familiar object that was presented with the novel object.

@@

We tested a total number of `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls). Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1). All children were recruited from the floor of a Children’s museum in San José, California, USA. This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status. Parents consented to their children’s participation and provided demographic information. All experiments were approved by the Stanford Institutional Review Board (protocol no. 19960)

@@

The experiment was presented as an interactive picture book on a tablet computer [@frank2016using]. Figure \@ref(fig:fig1)A shows the general setup. Children saw an animal between two tables. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests. Each experiment started with two training trials in which the speaker requested a known object (car and ball).

In Experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study). The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?". Children responded by touching one of the objects. The location of the novel object (left or right table) and the animal character were counterbalanced. Each child received 12 trials, one with each familiar object. The novel object also changed from trial to trial. We coded as correct choice if children chose the novel object as the referent of the novel word.

@@

Each child completed 12 trials, each with a different familiar and a different novel object. Familiar objects were selected to vary along the dimension of how likely children were to know the word for each object. This including objects that most 2-year-olds could name (e.g. a duck) as well as objects that only very few 5-year-olds could name (e.g. a pawn). The selection was based on age of acquisition ratings from Kuperman and colleagues [-@kuperman2012age]. While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned. Figure \@ref(fig:fig2)A shows the objects used in the experiment. We induced this variation to estimate the role of semantic knowledge in a mutual exclusivity inference.

@@

# prior_me <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")

@@

talk about sd around item as evidence for variation

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. As priors we used `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects\footnote{We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent.}. The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`\footnote{We did not pre-register agent as a random effect, but decided to included it to be consistent with Experiment 2 and 3.}. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and shows that there was substantial variation between them. Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept. The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the mutual exclusivity inference depended on age as well as the familiar object.

@@

Here we tested children's sensitivity to common ground that is build up over the course of a conversation. In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two]. The main goal of the experiment was to measure how children's sensitivity to common ground changes with age.

@@

The general setup was the same as in Experiment 1. The speaker was positioned between the tables. There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second novel object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B). The positioning of the novel object in the beginning of the experiment as well as the location the speaker turned to first was counterbalanced. Children received five trials, each with a different pair of novel objects. We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.

@@

```{r}
# prior_cg <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = prior_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_cg,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_cg.rds")

@@

To directly investigate whether children's response changed with age, we modeled the trial by trial data using a Bayesian GLMM (formula: `correct ~ age + (1 | id) + (age | speaker)`, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)). The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_cg%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_cg%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_cg%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`, see Figure \@ref(fig:fig3)A). Older children were more likely to chose the object that was new to the speaker as the referent of the novel word, suggesting that the sensitivity to common ground in this context increases with age.

## Experiment 3: Integration

Experiment 3 combined the procedures from Experiment 1 and 2. As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but also the role that each object (novel and familiar) had played in the preceding interaction. Combining the two procedures created two conditions: In the *congruent* condition, the novel object was also the object that was new to the speaker. In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent. In the *incongurent condition*, the familiar object was new to the speaker. Int his case, the two inferences pointed to different objects. The main focus of the overall study was to model how children integrate and balance these different information sources. We investigate this question in depth in the [modelling](#model) section below. Here, we limit the discussion to whether children differentiated between the two conditions.

@@

Experiment 3 followed the same procedure as Experiment 2 but involved the same objects as Experiment 1. In the beginning, one table was empty while there was an object (novel or familiar) on the other one. After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel). Next, the speaker re-appeared and made the usual request.

In the congruent condition, the familiar object was present in the beginning and the novel object appeared while the speaker was away (Figure \@ref(fig:fig1)C - left). In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent. In the incongruent condition, the novel object was present in the beginning and the familiar object appeared later. In this case, the two inferences pointed to different objects (Figure \@ref(fig:fig1)C - right).

Participants received up to 12 test trials, six in each condition, each with a different familiar and novel object. Familiar objects were the same as in Experiment 1. The positioning of the objects on the tables and the location the speaker first turned to were counterbalanced. Participants could stop the experiment after six trials (three per condition). If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per cell.

@@

All results are reported from the perspective of the mutual exclusivity inference (`correct` in the model formula below). In the incongruent condition, high proportions speak to a mutual exclusivity inference and low proportion for a common ground inference. In the congruent condition, both inferences pointed in the same direction. The focus of this experiment was on information integration and we therefore did not compare the performance to chance.

@@

# prior_comb <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# bm_comb <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | item)+ (age * alignment | agent),
#                     data = comb_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_comb,
#           cores = 4,
#           chains = 4,
#           inits = 0,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_comb.rds")

@@

plot_comb <- ggplot(plot_comb_map, aes(x=age,y = y, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(data = comb_data%>%left_join(aoa_ratings)%>%ungroup()%>%mutate(item = fct_reorder(factor(item), mean_aoa)), aes(x = age_num, y= correct, col = item), width = .00, height = .04, alpha = .2)+
  geom_line(size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~condition)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "Object")

@@

Use sd on item to say tha items vary substantially and sd on interaction or age to say they differ in their slope

We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | item) + (age * alignment | agent)`\footnote{We pre-registered to include item as a fixed effect in Experiment 3. The corresponding model was too complex to be constrained by the data. Furthermore, as explained in Experiment 1, items were chosen based on their rated age of acquisition. That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge.}, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)). The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children differentiated between the two conditions. The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`). Figure \@ref(fig:fig3)B visualizes the model. Taken together, the results show that children responded to the way the two inferences were aligned with one another. For the remainder of the study, we address the question of how the two inferences might have interacted with one another.

@@

@@

The main purpose of the study was to study *how* children integrate different information sources during word learning. To address this question, we use Bayesian cognitive models of prgamatic reasoning. We first describe an *integration model* which we think best represents the inference and integration processes. We then specify how this model captures developmental change.

Next, we ask how well this model *predicts* how children integrate the two information sources. That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about how they will be comined. Importantly, we ask this question before any data on integration has been collected. The model offers an answer and also allows us to make quantitative predictions. We can then test the predictive power of the model by comparing the model predictions to newly collected data. We will use model comparisons to test the *integration model* against a range of alternative models.

Finally, we ask how well our model *explains* the way that children integrate the two information sources. For this analysis, we fit the free parameters in the model to all the available data, those from experiment 1 and 2 as well as the integration data from experiment 3. We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops. This approach answers the question of how we can best explain how children are integrating the different information sources.

## Modelling framework

We implemented the cognitive models in the Rational Speech Act (RSA) framework [@frank2012predicting; goodman2016pragmatic]. RSA models are models of pragmatic reasoning in that they treat language understanding as a special case of Bayesian social reasoning. A listener interprets an utterance by assuming it was produced by a cooperative speaker who had the goal to be informative. Being informative is defined as providing a message that would increase the probability of the listener inferring the speaker’s intended message. This notion of contextual informativeness captures the Gricean idea of cooperation between speaker and listener, and provides a first approximation to what we have described above as utterance-level pragmatic information.

--- model in math ---

## Loci of development

We can identify three potential loci of development in the model described above: semantic knowledge, expectations about speaker informativeness and common ground sensitivity. Each of theses components is represented by a parameter in the model. We capture developmental change by making these parameters a function of age and estimate the developmental trajectory for each parameter. These age sensitive parameters are then passed through the model to generate predictions in the form of developmental trajectories for each item in the congruent and the incongruent condition.

@@

Semantic knowledge captures the degree of certainty with which the speaker and the (naive) listener know the label for the familiar object. The major source of variation in semantic knowledge are the different familiar objects. For objects whose labels are generally acquired earlier (e.g. carrot) semantic knowledge is high whereas for others (e.g. pawn) semantic knowledge is lower. However, semantic knowledge also varies with age in that older children are more likely to know the labels for more of the familiar objects compared to younger children. As a consequence, each familiar object has a unique developmental trajectory with respect to semantic knowledge.

@@

## Model fitting

All models were implemented in `webppl` [@dippl]. The corresponding model code can be found in the associated online repository. Model predictions and model comparison are based on the full posterior distribution for each model parameter.

@@

Estimate parameters based on me data and prior data. The models considered below make differential use of theses parameters. Basically, one full model and the rest are lesion model

### Model parameters

# parameter distributions based on model 
item_params <- readRDS("../saves/item_params.rds")
global_params <- readRDS("../saves/global_params.rds")
item_sigma <- readRDS("../saves/item_sigma.rds")

# summaries
item_params_summary <- item_params %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary <- global_params %>%
  group_by (parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

# selection object
select <- sample(1:length(unique(global_params$iteration)), 30)

# plot for semantic knowledge

sem_know_map <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  expand_grid(., age = unique(me_data$age)) %>%
  mutate(sem_know = plogis(intercept + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

plot_sem_know <- ggplot()+
  geom_line(data = sem_know_map, aes(x = age+2, y= sem_know, col = item, group = item),size = 1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_colour_viridis_d(name = "Object")

# plot or speaker optimality

speak_opt <- global_params%>%
  filter(parameter == "speaker_optimality")

speak_opt_line <- speak_opt%>%
  filter(iteration %in% select)%>%
  spread(type, value)%>%
  expand_grid(., age = unique(me_data$age))%>%
  mutate(y = intercept + slope * age)

speak_opt_map <- global_params_summary%>%
  ungroup()%>%
  filter(parameter == "speaker_optimality")%>%
  select(type, mode)%>%
  spread(type, mode)%>%
  expand_grid(., age = unique(me_data$age))%>%
  mutate(y = intercept + slope * age)

plot_speak_opt <- ggplot() +
  geom_line(data = speak_opt_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
  geom_line(data = speak_opt_map, aes(x=age+2,y = y),size = 1)+
  labs(x="Age",y="Speaker informativeness")+
  theme_few() +
  ylim(0,10)+
    xlim(2,5)+
  guides(alpha = F, fill = F, col = F)

# Plot prior sensitivity

prior <- global_params%>%
  filter(parameter == "prior")

prior_line <- prior%>%
  filter(iteration %in% select)%>%
  spread(type, value)%>%
  expand_grid(., age = unique(me_data$age))%>%
  mutate(y = plogis(intercept + slope * age))

prior_map <- global_params_summary%>%
  ungroup()%>%
  filter(parameter == "prior")%>%
  select(type, mode)%>%
  spread(type, mode)%>%
  expand_grid(., age = unique(me_data$age))%>%
  mutate(y = plogis(intercept + slope * age))

plot_prior <- ggplot() +
  geom_line(data = prior_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
  geom_line(data = prior_map, aes(x=age+2,y = y),size = 1)+
  labs(x="Age",y="Prior sensitivity")+
  theme_few() +
  ylim(0,1)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)

```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity. Solid lines in show the MAP estimate for each parameter. Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty. (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.1,1,1))
```

### Integration model

@@

semantic knowledge is only a function of age and not specific to the item. Roughly corresponds to. If children are vaguely familiar with an object, the make the ME inference regardless of the individual object

@@

range of log like across chains and then model comparison

@@

### Model parameters

# parameter distributions based on model 
item_params_exp <- readRDS("../saves/item_params_fb.rds")
global_params_exp <- readRDS("../saves/global_params_fb.rds")
item_sigma_exp <- readRDS("../saves/item_sigma_fb.rds")

# summaries
item_params_summary_exp <- item_params_exp %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary_exp <- global_params_exp %>%
  group_by (parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

# selection object
select_exp <- sample(1:length(unique(global_params_exp$iteration)), 30)

# plot for semantic knowledge

sem_know_map_exp <- item_params_summary_exp%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  expand_grid(., age = unique(comb_data$age)) %>%
  mutate(sem_know = plogis(intercept + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

plot_sem_know_exp <- ggplot()+
  geom_line(data = sem_know_map_exp, aes(x = age+2, y= sem_know, col = item, group = item),size = 1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_colour_viridis_d(name = "Object")

# plot or speaker optimality

speak_opt_exp <- global_params_exp%>%
  filter(parameter == "speaker_optimality")

speak_opt_line_exp <- speak_opt_exp%>%
  filter(iteration %in% select)%>%
  spread(type, value)%>%
  expand_grid(., age = unique(comb_data$age))%>%
  mutate(y = intercept + slope * age)

speak_opt_map_exp <- global_params_summary_exp%>%
  ungroup()%>%
  filter(parameter == "speaker_optimality")%>%
  select(type, mode)%>%
  spread(type, mode)%>%
  expand_grid(., age = unique(comb_data$age))%>%
  mutate(y = intercept + slope * age)

plot_speak_opt_exp <- ggplot() +
  geom_line(data = speak_opt_line_exp, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
  geom_line(data = speak_opt_map_exp, aes(x=age+2,y = y),size = 1)+
  labs(x="Age",y="Speaker informativeness")+
  theme_few() +
  ylim(0,10)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)

# Plot prior sensitivity

prior_exp <- global_params_exp%>%
  filter(parameter == "prior")

prior_line_exp <- prior_exp%>%
  filter(iteration %in% select)%>%
  spread(type, value)%>%
  expand_grid(., age = unique(comb_data$age))%>%
  mutate(y = plogis(intercept + slope * age))

prior_map_exp <- global_params_summary_exp%>%
  ungroup()%>%
  filter(parameter == "prior")%>%
  select(type, mode)%>%
  spread(type, mode)%>%
  expand_grid(., age = unique(comb_data$age))%>%
  mutate(y = plogis(intercept + slope * age))

plot_prior_exp <- ggplot() +
  geom_line(data = prior_line_exp, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
  geom_line(data = prior_map_exp, aes(x=age+2,y = y),size = 1)+
  labs(x="Age",y="Prior sensitivity")+
  theme_few() +
  ylim(0,1)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)
